---
title: "Rworksheet4A"
output:
  word_document: default
  pdf_document: default
date: "2023-10-25"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r setup, include=TRUE}

#1. The table below shows the data about shoe size and height. Create a data frame.
Shoe_size <-c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5,13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height<-c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0,77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0)

total <- data.frame(Shoe_size,Height)
total


#a. Describe the data. The data shows the corresponding shoe size per height.

Gender<-c("F","F","F","F","M","F","F","F","M","F","M","F","M","M","M","M","F","F","M","F","F","M","M","F","M","M","M","M")

#b. Create a subset by males and females with their corresponding shoe size and height.

total2 <- cbind(total,Gender)
total2

#What its result? Show the R scripts.
#Shoe_size Height Gender
#1        6.5   66.0      F
#2        9.0   68.0      F
#3        8.5   64.5      F
#4        8.5   65.0      F
#5       10.5   70.0      M
#6        7.0   64.0      F
#7        9.5   70.0      F
#8        9.0   71.0      F
#9       13.0   72.0      M
#10       7.5   64.0      F
#11      10.5   74.5      M
#12       8.5   67.0      F
#13      12.0   71.0      M
#14      10.5   71.0      M
#15      13.0   77.0      M
#16      11.5   72.0      M
#17       8.5   59.0      F
#18       5.0   62.0      F
#19      10.0   72.0      M
#20       6.5   66.0      F
#21       7.5   64.0      F
#22       8.5   67.0      M
#23      10.5   73.0      M
#24       8.5   69.0      F
#25      10.5   72.0      M
#26      11.0   70.0      M
#27       9.0   69.0      M
#28      13.0   70.0      M


#c. Find the mean of shoe size and height of the respondents.
size<-mean(Shoe_size)
size
height<-mean(Height)
height


#Write the R scripts and its result.
#> msize<-mean(Shoe_size)
#> msize
#[1] 9.410714
#> mheight<-mean(Height)
#> mheight
#[1] 68.57143


#d. Is there a relationship between shoe size and height? Why?
#The data suggests a potential relationship between shoe size and height, but further statistical analysis like correlation or regression is needed to confirm and understand this connection.


# Create a character vector of months
months <- c("March", "April", "January", "November", "January", "September", "October", "September", "November", "August", "January", "Nevember", "November", "February", "May", "August", "July", "December", "August", "August", "September", "November", "February", "April")
months
factor_months<-factor(months)
factor_months

 #3
factor_months_vector <-factor(months)
factor_months_vector
summary(factor_months_vector)
#Are they both equally useful in this case? yes

#4
direction<- c("East","West","North")
direction
frequency<- c(1,4,3)
frequency

#5
#a
file<- read.csv("import1_march.csv")
file
file2<-read.table("//cloud/project//import1_march.csv", header=TRUE,sep=",")
file2

#6
num <- readline(prompt = "Input randomly select numbers from 1 to 50: ")
if (num > 50){
  print('The number selected beyond the of 1 to 50')
}else if(num <=20){
  print('TRUE')
}
#7
#a
calculate_minimum_bills <- function(){
  price <-as.integer(readline(prompt = "Price of snack(a random number divisible by 50):"))
  if (is.na(price)|| price %% 50 !=0 ){
    cat("Invalid input. Please enter a valid price divisible by 50.\n")
    return ()
  }
    num_bills <- 0
    bill_denomination <-c(1000,500,200,100,50)
    
    for (bill in bill_denomination){
      num_bills <-num_bills+(price %% bill)
      price<- price %% bill
    }
    cat("Minimum number of bills needed: ",num_bills, "\n")
  }
  calculate_minimum_bills()

#8
  #a
  name<- c( "Annie" , "Thea" , "Steve" , "Hanna" )
  grade1 <-c(85,86,75,95)
  grade2 <-c(65,75,55,75)
  grade3 <-c(85,90,80,100)
  grade4 <-c(95,75,100,100)
  card <-data.frame(name,grade1,grade2,grade3,grade4)
  card
#b
  for (i in 1:length(name)){
    average <-(grade1[i]+grade2[i]+grade3[i]+grade4[i]) / 4
    cat(paste(name [i],"average of this semester is",round(average,2),".\n"))
  }
#c
  for(test_num in 1:4){
    total <-grade1+grade2+grade3+grade4
    average <-total/4
     
    if (average[test_num]<80){
      cat("The", test_num,"test was difficult.\n")
    }
  }
#d
  for (i in 1:length(name)){
    highest_grade <- grade1[i]
    if (grade2[i] > highest_grade){
      highest_grade <- grade2[i]
    }
    if (grade3[i] > highest_grade){
      highest_grade <- grade3[i]
    }
    if (grade4[i] > highest_grade){  
      highest_grade <- grade4[i]  
    }
    
    if (highest_grade > 90){
      cat(paste(name[i], "'s highest grade this semester is", highest_grade,".\n"))
    }
  }
  
  
  
  